Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-15 paper/Comparing-belief-in-free-will-and-job-satisfaction-in-the-US-and-Taiwan.qmd
test
Update Comparing-belief-in-free-will-and-job-satisfaction-in-the-US-and-Taiwan.qmd

## 2.1 Source
	The paper we have used for replication is from the list of Gilad Feldman 
	papers offered from the course, specifically titled Agency Beliefs Over Time 
	and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction, 
	written by Gilad Feldman, Jiing-Lih Farh, and Kin Fai Ellick Wong. This paper 
	dives into the meanings of free will, and takes several studies examining its 
	correlation with job satisfaction as the primary factor, but also includes 
	ideas in regards to psychological well-being and international perspectives. 
	Our reproduction seeks to focus on two different findings made from the 
	original paper and apply a holistic lens to it. 
	The two claims we are focusing on are as follows: (1) Is there a positive or 
	negative relationship between free will and job satisfaction? (2) Something 
	about age 
## 2.2 Methodology 
	This paper replicates the data that was originally studied for the (2018) 
	paper Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict 
	Higher Job Satisfaction. The first study takes Taiwanese real estate agent’s 
	job satisfaction into account and conducted the study in 54 branch offices of 
	a public real estate company based in Taiwan. They then proceeded by
	distributing the surveys to agents in each of the branches at two different 
	times, once every 3 months for a total of 6 months of data. They ended up with
	293 surveys to review for study #1. For study number #2, the paper looks into 
	the Amazon Mechanical Turk (MTurk) American Worker’s Job Satisfaction. 
	The study was conducted in two different sections, in which they were able 
	to survey a total of 209 American participants. After this initial study was 
	done, the same group was invited to conduct a follow-up survey six months 
	later and took in responses over 15 days. Out of the 209 initial participants,
	only 137 of them conducted the follow-up survey. And for the final study, 
	contrary to the first two where they directly went to a group and surveyed 
	them; the surveyors used previous data from the World Value Survey (WVS) which
	was data conducted between 1990 and 2008, looking into the participant's views
	on free will, job satisfaction, and job autonomy. Over these 18 years, 
	the survey received data 257,597 people, and focused on 14,062 participants as
	they answered questions directly related to our research. Although the total 
	survey took into account people from over 40 countries, for our focus 
	we looked at individuals from 16 specific countries. 
## 2.3 Features 
	The studies conducted each had their specific variables conducted. 
	For the first study, the survey takes into account age, gender, social 
	desirability of the job, job satisfaction after the first wave of surveys, job satisfaction after the second wave of surveys, and their beliefs on free will. 
	The age range for this study was between 22 to 49 years old, and only took 
	into account male and female genders. The second study primarily took free 
	will and job satisfaction into account.

>>>>

## 2.1 Source
	The paper we have used for replication is from the list of Gilad Feldman 
	papers offered from the course, specifically titled Agency Beliefs Over Time 
	and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction, 
	written by Gilad Feldman, Jiing-Lih Farh, and Kin Fai Ellick Wong. This paper 
	dives into the meanings of free will, and takes several studies examining its 
	correlation with job satisfaction as the primary factor, but also includes 
	ideas in regards to psychological well-being and international perspectives. 
	Our reproduction seeks to focus on two different findings made from the 
	original paper and apply a holistic lens to it. 
	The two claims we are focusing on are as follows: (1) Assessing the direction of the relationship between belief in free will and job satisfaction. (2) Evaluating the impact of cultural contexts on the perception of free will on indivudals throughout different professions and age groups.

## 2.2 Methodology 
	This paper replicates the data that was originally studied for the (2018) 
	paper Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict 
	Higher Job Satisfaction. The first study takes Taiwanese real estate agent’s 
	job satisfaction into account and conducted the study in 54 branch offices of 
	a public real estate company based in Taiwan. They then proceeded by
	distributing the surveys to agents in each of the branches at two different 
	times, once every 3 months for a total of 6 months of data. They ended up with
	293 surveys to review for study #1. For study number #2, the paper looks into 
	the Amazon Mechanical Turk (MTurk) American Worker’s Job Satisfaction. 
	The study was conducted in two different sections, in which they were able 
	to survey a total of 209 American participants. After this initial study was 
	done, the same group was invited to conduct a follow-up survey six months 
	later and took in responses over 15 days. Out of the 209 initial participants,
	only 137 of them conducted the follow-up survey. And for the final study, 
	contrary to the first two where they directly went to a group and surveyed 
	them; the surveyors used previous data from the World Value Survey (WVS) which
	was data conducted between 1990 and 2008, looking into the participant's views
	on free will, job satisfaction, and job autonomy. Over these 18 years, 
	the survey received data 257,597 people, and focused on 14,062 participants as
	they answered questions directly related to our research. Although the total 
	survey took into account people from over 40 countries, for our focus 
	we looked at individuals from 16 specific countries. 
## 2.3 Features 
	The studies conducted each had their specific variables conducted. 
	For the first study, the survey takes into account age, gender, social 
	desirability of the job, job satisfaction after the first wave of surveys, job satisfaction after the second wave of surveys, and their beliefs on free will. 
	The age range for this study was between 22 to 49 years old, and only took 
	into account male and female genders. The second study primarily took free 
	will and job satisfaction into account.
